\documentclass{article}
\usepackage[utf8]{inputenc}


\usepackage{float}
\usepackage{listings}
\usepackage{url}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{wrapfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage[export]{adjustbox}

\newcommand{\ninanotes}[1]{{\color{red} #1}}
\newcommand{\mytodonswer}[1]{{\color{brown} #1}}
\newcommand{\plan}[1]{{\colorbox{cyan} {#1}}}

\newcommand{\KTfourfiveN}{KT$45^n$}

% \newcommand{\typenaturalnumbers}{\mathbb{N}_0}

% \usepackage{natbib}

\title{Bachelor report}
\author{s174256 }
\date{February 2023}

\begin{document}

\ninanotes{
The form and content of a report depend on a number of things:
\begin{itemize}
\item The subject/problem the report deals with.
\item The role of the author (observer, solver, advisor).
\item The report can be an instruction manual, a maintenance manual, a guide to repeat a process, etc.
\item The target audience (level of pre-knowledge, is shallow or deep information required).
\item Are there different target groups needing different information?
\item Physical restrictions (size, media used, etc).
\end{itemize}

\mytodonswer{
	\begin{itemize}
\item Hanabi complexity, optimization and zig
\item Solver
\item Design and implementation decisions
\item The level of preknowledge should be basic computerscience knowledge, basic algorithms, basic compiler knowledge.
\item no, just CS professors
\item 20 pages it seems like :)
	\end{itemize}

}

What to document?:
\begin{itemize}
	\item What is the problem to be solved?
	\item Is the problem specified well enough? Otherwise find a sound,
unambiguous definition.
\item What is needed to solve the problem?
\item How is the solution structured?
\item How is the solution implemented?
\item What impact will the solution have on whom?
\end{itemize}

Problemanalysis
\begin{itemize}
\item Check whether the given problem description is clear and the goal is
well-defined and unambiguous.
\item Make a problem description which meets these requirements. Have the
reader in mind, not only the writers.
\item If needed, invent your own terms to make the description clear, BUT
describe them to the reader (e.g., in a glossary), not just use them.
When the original description is vague, this requires a drop in
abstraction when concretising.
\item In the same way formulate the goal(s) and the conditions when a goal is
reached.
\end{itemize}
}

\maketitle
\newpage
\tableofcontents
\include{00_introduction.tex}
\include{01_problem_analysis_and_succes_criteria.tex}
\include{02_design.tex}
\include{03_implementation.tex}
\include{04_testing.tex}
\include{05_project_management.tex}
\include{06_conclusion.tex}
% \oesuntaeoushnt
\bibliographystyle{plain}
\bibliography{bib.bib}
\appendix
\include{appendix.tex}
\end{document}
